---
title: 'DE Analysis: Phenotypes'
author: "Adam Festa"
date: "5/12/2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Script objective

The purpose of this script is to conduct differntial expression on all families which have phenotypes, examinining the differences between the extreme ends of the phenotypic distribution.

```{r cars}
suppressPackageStartupMessages(library(DESeq2))
```

## Load output from previous run

```{r}
load("/mnt/media/disk6/ARF/DiffExpression/ddstxi_bio_0.v2.RData")
```


## Load pedigree origin table

The Rdata object loaded below was generated using the `create_fam_origin_table.R` script located in the `/resources/pedigree` directory.

```{r}
 load("/mnt/media/disk6/ARF/DiffExpression/RNAseq-DE-analysis/resources/pedigree/fam_origins.Rdata")
```


## Create contrasts between States

```{r wg.states}
# WG.FL ####
wg.fams <- as.character(fam.origins$family)[which(fam.origins$state == "TX")]
fl.fams <- as.character(fam.origins$family)[which(fam.origins$state == "FL")]
fl.fams <- paste0("fam_id",fl.fams)
wg.fams <- paste0("fam_id",wg.fams)

which(resultsNames(ddsTxi) %in% fl.fams)

cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% fl.fams)] <- 1/length(fl.fams)
cons[which(resultsNames(ddsTxi) %in% wg.fams)] <- (1/length(wg.fams))*-1


library(BiocParallel)
register(MulticoreParam(30))
fl.wg <- results(object = ddsTxi,contrast = cons,parallel = T)

summary(fl.wg)


# WG.SC ####
sc.fams <- as.character(fam.origins$family)[which(fam.origins$state == "SC")]
sc.fams <- paste0("fam_id",sc.fams)

cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% sc.fams)] <- 1/length(sc.fams)
cons[which(resultsNames(ddsTxi) %in% wg.fams)] <- (1/length(wg.fams))*-1

library(BiocParallel)
register(MulticoreParam(30))
sc.wg <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(sc.wg)

# WG.GA ####
ga.fams <- as.character(fam.origins$family)[which(fam.origins$state == "GA")]
ga.fams <- paste0("fam_id",ga.fams)

cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% ga.fams)] <- 1/length(ga.fams)
cons[which(resultsNames(ddsTxi) %in% wg.fams)] <- (1/length(wg.fams))*-1

register(MulticoreParam(30))
ga.wg <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(ga.wg)

# WG.NC ####
nc.fams <- as.character(fam.origins$family)[which(fam.origins$state == "NC")]
nc.fams <- paste0("fam_id",nc.fams)

cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% nc.fams)] <- 1/length(nc.fams)
cons[which(resultsNames(ddsTxi) %in% wg.fams)] <- (1/length(wg.fams))*-1

library(BiocParallel)
register(MulticoreParam(30))
nc.wg <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(nc.wg)

```

```{r nc.comps}
# NC.FL ####
cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% nc.fams)] <- (1/length(nc.fams))*-1
cons[which(resultsNames(ddsTxi) %in% fl.fams)] <- 1/length(fl.fams)

register(MulticoreParam(30))
fl.nc <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(fl.nc)

# NC.SC ####
cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% sc.fams)] <- 1/length(sc.fams)
cons[which(resultsNames(ddsTxi) %in% nc.fams)] <- (1/length(nc.fams))*-1

register(MulticoreParam(30))
sc.nc <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(sc.nc)

# NC.GA ####
cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% ga.fams)] <- 1/length(ga.fams)
cons[which(resultsNames(ddsTxi) %in% nc.fams)] <- (1/length(nc.fams))*-1

register(MulticoreParam(30))
ga.nc <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(ga.nc)

```

```{r sc.comps}
# SC.FL ####
cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% sc.fams)] <- (1/length(sc.fams))*-1
cons[which(resultsNames(ddsTxi) %in% fl.fams)] <- 1/length(fl.fams)

register(MulticoreParam(30))
fl.sc <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(fl.sc)

# SC.GA ####
cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% ga.fams)] <- 1/length(ga.fams)
cons[which(resultsNames(ddsTxi) %in% sc.fams)] <- (1/length(sc.fams))*-1

register(MulticoreParam(30))
ga.sc <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(ga.sc)

```

```{r fl.comps}
# FL.GA ####
cons <- rep(0,length(resultsNames(ddsTxi)))
cons[which(resultsNames(ddsTxi) %in% ga.fams)] <- 1/length(ga.fams)
cons[which(resultsNames(ddsTxi) %in% fl.fams)] <- (1/length(fl.fams))*-1

register(MulticoreParam(30))
ga.fl <- results(object = ddsTxi,contrast = cons,parallel = T)
summary(ga.fl)
```


## Save image

```{r save}
save.image(file = "/mnt/media/disk6/ARF/DiffExpression/DESEQ2_bio.0_states.RData",compress = T)
```